Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
minor wording, specifics

In addition to the number of failed contract checks, we were interested in
how many functions had a parameter where a contract check failed, and
overall we found this to be the case in \PROPFUNSFAILEDCHECK of functions.
Digging a little deeper, we noticed that many of these functions were
performing S3 dispatch which we do not handle.  Removing those functions, we
see that \PROPFUNSFAILEDCHECKNOSTHREE of functions exhibited failing
contract checks.  These are functions were likely under-tested, as calls to
these functions represent only \PERCCALLSBADFUNSINTESTS of recorded calls
during \typetracer's run on the core corpus to infer types.

>>>>

In addition to the number of failed contract checks, we were interested in
how many functions had a parameter where a contract check failed, and
overall we found this to be the case in \PROPFUNSFAILEDCHECK of functions.
To subdivide this number, we discounted functions that were performing S3
dispatch, as they exhibit user-defined polymorphism which we do not handle.
Removing those functions, we see that the proportion of functions with failed contract checks falls to 
\PROPFUNSFAILEDCHECKNOSTHREE. These remaining functions were under-tested, as calls to
these functions represent only \PERCCALLSBADFUNSINTESTS of recorded calls
during \typetracer's run on the core corpus to infer types.
